Using evolutionary algorithms to optimize the estimation of a diffusion process

### 2015-01-24 paperGecco.tex
Cambio Formato 1

\begin{enumerate}
\item First, it selects a set of neighbourhood structures $\mathcal N_k$, $k=1,\cdots,k_{max}$, and random distributions for the (2.b.i) step, that will be used in the search, and it finds an initial solution $x$.
\item It repeats the following sequence until a stopping condition is met:
    \begin{enumerate}
        \item Set $k\leftarrow 1$;
        \item Repeat the following steps until $k>k_{max}$:
        \begin{enumerate}
            \item Generate a point $y$ randomly from the $k-$th neighbourhood of $x$ $(y\in\mathcal N_{k}(x))$;
                \item Apply some local search method with $y$ as initial solution to obtain a local optimum given by $y´$;
                \item If the local optimum is better than the incumbent, move there $(x\leftarrow y´)$, and continue the search with $\mathcal N_1 (k\leftarrow 1)$; otherwise, set $k\leftarrow k+1$.
        \end{enumerate}
    \end{enumerate}

@@

%The authors would like to thank the FEDER of European Union for financial support via project ``Sistema de Informaci{\'o}n y Predicci{\'o}n de bajo coste y aut{\'o}nomo para conocer el Estado de las Carreteras en tiempo real mediante dispositivos distribuidos" (SIPEsCa) of the ``Programa Operativo FEDER de Andaluc\'{i}a 2007-2013". We also thank all Agency of Public Works of Andalusia Regional Government staff and researchers for their dedication and their professionalism. This work has been supported in part by project ANYSELF (TIN2011-28627-C04-02) and MICINN (Spain) MTM2011-28962.
%\begin{figure}
%\begin{center}
%\epsfig{file=sipesca_2.eps,width=4cm}
%\end{center}
%\end{figure}

\bibliographystyle{plain}
%\bibliography{my_papers,gprop,maribel}

\begin{thebibliography}{10}

\bibitem{proceedingBol}
Guti{\'e}rrez, R., Rico, N., Rom{\'a}n, P., Romero, D., Torres, F.:
Un nuevo proceso de difusi{\'o}n para modelizar patrones de crecimiento mixto exponencial-Gompertz. XXX Congreso Nacional SEIO. Libro de Actas, pp. 1--15 (2007)

\bibitem{Gut07b}
Guti{\'e}rrez, R., Rom{\'a}n, P., Romero, D., Serrano, J.J. y Torres, F.:
A new Gompertz-type diffusion process with application to random growth. Math. Biosci. 208,147--165 (2007)

\bibitem{GutCy}
Guti{\'e}rrez, R., Rom{\'a}n, P., Romero, D. and Torres, F.:
Applications of the univariate lognormal diffusion process with exogenous factors in forecasting. {Cybernet Syst.} {34}(8),709--724 (2003)

\bibitem{Gut99} Guti{\'e}rrez, R., Rom{\'a}n, P. and Torres, F.:
Inference and first-passage-times for the lognormal diffusion process with exogenous factors: application to modelling
in economics. Appl. Soch. Model. Bus. {15},325-332 (1999)

\bibitem{SA}
Ingber, L.:
Simulated annealing: Practice versus theory. Mathl. Comput. Modelling, vol. 18(11), pp. 29--57 (1993)

\bibitem{Kirkpatrick83}
S. Kirkpatrick1, C. D. Gelatt Jr. M. P. Vecch:
Optimization by Simulated Annealing. Science Vol. 220 no. 4598 pp. 671-680 (1983)

\bibitem{Michalewicz96}
Zbigniew Michalewicz:
Heuristic methods for evolutionary computation techniques. J. Heuristics 1(2):177-206 (1996)

\bibitem{EA}
B{\"{a}}ck, T.:
Evolutionary algorithms in theory and practice, Oxford University Press (1996)

\bibitem{Kloeden}
Kloeden, P. E., Platen, E. y Schurz, H.:
Numerical solution of SDE through computer experiments, {Springer-Verlag} (1994)

\bibitem{Rao}
Rao, N. J., Borwankar, J. D. y Ramkrishna, D.:
Numerical solution of Ito integral equations. {SIAM Journal on Control and Optimization} {12}, 124--139 (1974)

\bibitem{error}
De Gooijer, J.G., Hyndman, R.J.:
25 Years of IIF Time Series Forecasting: A Selective Review. Tinbergen Institute Discussion Papers No. TI 05-068/4 . (2005)

\bibitem{GProp}
P. A. Castillo, J. Carpio, J. J. Merelo, V. Rivas, G. Romero, and A. Prieto:
Evolving Multilayer Perceptrons, Neural Processing Letters, vol. 12, no. 2, pp. 115{\^a}€“127, 2000.

\bibitem{GPropII}
S. Fahlman:
Faster-learning variations on back-propagation: An empirical study, in Proceedings of the 1988 Connection- ist models summer school. M. Kaufmann, 1988, pp. 38{\^a}€“51.

\bibitem{lognormal}
Log-normal Distributions across the Sciences: Keys and Clues
Article in Bioscience 51, No. 5, May 2001, 341-352.

\bibitem{blx}
Manuel Lozano, Francisco Herrera, Natalio Krasnogor, and Daniel Molina:
Real-coded memetic algorithms with crossover hill-climbing. Evol. Comput. 12, 3. Sep, 2004, 273-302.

\bibitem{VNS} Mladenovic´, N. and Hansen, P.: Variable neighborhood search. {Computers and Operations Research} {24}, 1097--1100 (1997)

\end{thebibliography}
\end{document}

>>>>

\begin{enumerate}
\item First, it selects a set of neighbourhood structures $\mathcal N_k$, $k=1,\cdots,k_{max}$, and random distributions for the (2.b.i) step, that will be used in the search, and it finds an initial solution $x$.
\item It repeats the following sequence until a stopping condition is met:
    \begin{enumerate}
        \item Set $k\leftarrow 1$;
        \item Repeat the following steps until $k>k_{max}$:
        \begin{enumerate}
            \item Generate a point $y$ randomly from the $k-$th neighbourhood of $x$ $(y\in\mathcal N_{k}(x))$;
                \item Apply some local search method with $y$ as initial solution to obtain a local optimum given by $yŽ$;
                \item If the local optimum is better than the incumbent, move there $(x\leftarrow yŽ)$, and continue the search with $\mathcal N_1 (k\leftarrow 1)$; otherwise, set $k\leftarrow k+1$.
        \end{enumerate}
    \end{enumerate}

@@

%The authors would like to thank the FEDER of European Union for financial support via project ``Sistema de Informaci{\'o}n y Predicci{\'o}n de bajo coste y aut{\'o}nomo para conocer el Estado de las Carreteras en tiempo real mediante dispositivos distribuidos" (SIPEsCa) of the ``Programa Operativo FEDER de Andaluc\'{i}a 2007-2013". We also thank all Agency of Public Works of Andalusia Regional Government staff and researchers for their dedication and their professionalism. This work has been supported in part by project ANYSELF (TIN2011-28627-C04-02) and MICINN (Spain) MTM2011-28962.
%\begin{figure}
%\begin{center}
%\epsfig{file=sipesca_2.eps,width=4cm}
%\end{center}
%\end{figure}
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case

\end{document}
